% Resume - Matheus Daher
% Add portfolio link to heading

\documentclass[letterpaper,12pt]{fed-res}
\begin{document}

%-------------------------------------------------------------------------------
% HEADING
%-------------------------------------------------------------------------------
\begin{center}
    \textbf{\Huge \scshape Matheus Daher} \\ \vspace{2pt}
    Toronto, ON, Canada \\ \vspace{2pt}
    +1 (437) 660-3537 \ $|$ \ mthsvdaher@gmail.com \\ \vspace{2pt}
    \href{https://github.com/mthsdaher}{github.com/mthsdaher} \ $|$ \
    \href{https://www.linkedin.com/in/matheus-daher/}{linkedin.com/in/matheus-daher} \ $|$ \
    \href{https://portfolio-git-main-matheus-projects-cba512cb.vercel.app/}{portfolio}
\end{center}

%-------------------------------------------------------------------------------
% OBJECTIVE
%-------------------------------------------------------------------------------
\section{Objective}
Full-Stack Developer focused on TypeScript, React, and Node.js, seeking software opportunities in Canada to build reliable, user-centred products with robust API validation and maintainable architecture.

%-------------------------------------------------------------------------------
% SKILLS
%-------------------------------------------------------------------------------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \item \textbf{Languages:} TypeScript, JavaScript, SQL, HTML, CSS
  \item \textbf{Frontend:} React, React Native, Vite, Hooks, Context API, Tailwind CSS
  \item \textbf{Backend:} Node.js, Express.js, REST APIs, Zod, express-validator, JWT
  \item \textbf{Data/Cloud:} PostgreSQL, MySQL, MongoDB Atlas, Google Cloud Run
  \item \textbf{Tools:} Git, GitHub, Docker, GitHub Actions, Swagger/OpenAPI, Postman
\end{itemize}

%-------------------------------------------------------------------------------
% EXPERIENCE
%-------------------------------------------------------------------------------
\section{Professional Experience}

\textbf{Full-Stack Developer} \hfill Sep 2024 -- Present \\
\textit{Povo App, Toronto, ON}
\begin{itemize}[leftmargin=0.15in]
  \item Customized AdminJS dashboards and resource views to improve visibility across users, businesses, and products.
  \item Optimized MySQL schema and queries (joins/indexes) to support high-performance data access.
  \item Built secure Express.js APIs with validation and documented endpoints using Swagger/OpenAPI.
\end{itemize}

\textbf{Construction Assistant / Admin Coordinator} \hfill Sep 2024 -- Present \\
\textit{Stewart Contracting, Toronto, ON}
\begin{itemize}[leftmargin=0.15in]
  \item Automated estimates/invoicing workflows with Excel/VBA, reducing turnaround time by 60\%.
  \item Built internal tracking tools for labour and materials to improve operational decision-making.
\end{itemize}

%-------------------------------------------------------------------------------
% PROJECTS
%-------------------------------------------------------------------------------
\section{Projects}

\textbf{Receipt-Scanner} \hfill
\href{https://github.com/mthsdaher/receipt-scanner}{GitHub}
\begin{itemize}[leftmargin=0.15in]
  \item Built a receipt-processing workflow to transform raw inputs into structured, searchable records.
  \item Implemented typed contracts and validation across client/server layers to improve consistency.
  \item \textbf{Stack:} TypeScript, React, Node.js, Express, Zod.
\end{itemize}

\textbf{Agendamento Unique} \hfill
\href{https://agendamento-unique-655344779408.northamerica-northeast2.run.app/}{Live Demo}
\begin{itemize}[leftmargin=0.15in]
  \item Developed a centralized booking platform for courts, events, and parties with conflict prevention flows.
  \item Built responsive interfaces and backend endpoints for reliable reservation operations.
  \item \textbf{Stack:} TypeScript, React, Node.js, Express, Zod, Google Cloud Run.
\end{itemize}

%-------------------------------------------------------------------------------
% CERTIFICATION
%-------------------------------------------------------------------------------
\section{Certification}
\textbf{Microservices with Node JS and React} \hfill Udemy, Completed Apr 20, 2025 \\
Certificate confirms full course completion, including all video and article modules.

%-------------------------------------------------------------------------------
% EDUCATION
%-------------------------------------------------------------------------------
\section{Education}
\textbf{Computer Programming} \hfill Graduated Apr 2025 \\
Georgian College at ILAC, Toronto, ON \hfill GPA: 3.5+

\textbf{Civil Engineering} \hfill Graduated Jun 2020 \\
Estacio de Sa, Brazil

\end{document}
